Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-02-17 paper/manuscript.tex
Updates from Overleaf

The standard Gibbs free energy of binding between a receptor $R$ and a ligand $L$ to form a complex $RL$ in a solvent $v$
\begin{equation}
  R(v) + L(v)  \leftrightharpoons RL(v)
  \label{eq:binding-reaction}
\end{equation}
is
\begin{equation}
  \Delta G^\circ_{b} = \mu^\circ_{RL(v)}  - \mu^\circ_{R(v)} - \mu^\circ_{L(v)} = -k_B T \ln Kb 
  \label{eq:DG0-binding-def}
\end{equation}
where~\cite{gilson1997statisticalthermodynamic,gilson2007calculation}
\begin{equation}
  Kb = \frac{C^\circ}{8 \pi^2} \frac{z_{RL(v)}}{z_{R(v)} z_{L(v)}}
  \label{eq:DG0-binding-constant-def}
\end{equation}
is the statistical mechanics expression for the binding constant. Eq.~(\ref{eq:DG0-binding-constant-def}) follows from the application of  Eq.~(\ref{eq:chemical-potential-standard}) for each of the three species and noting that the contributions of the momenta cancel. As discussed below, various alchemical protocols exist to evaluate the ratios of partition functions in Eq.~(\ref{eq:DG0-binding-constant-def}}), providing a connection between the theory and observed binding affinities.

>>>>

The standard Gibbs free energy of binding between a receptor $R$ and a ligand $L$ to form a complex $RL$ in a solvent $v$
\begin{equation}
  R(v) + L(v)  \leftrightharpoons RL(v)
  \label{eq:binding-reaction}
\end{equation}
is
\begin{equation}
  \Delta G^\circ_{b} = \mu^\circ_{RL(v)}  - \mu^\circ_{R(v)} - \mu^\circ_{L(v)} = -k_B T \ln Kb 
  \label{eq:DG0-binding-def}
\end{equation}
where~\cite{gilson1997statisticalthermodynamic,gilson2007calculation}
\begin{equation}
  Kb = \frac{C^\circ}{8 \pi^2} \frac{z_{RL(v)}}{z_{R(v)} z_{L(v)}}
  \label{eq:DG0-binding-constant-def}
\end{equation}
is the statistical mechanics expression for the binding constant. Eq.~(\ref{eq:DG0-binding-constant-def}) follows from the application of  Eq.~(\ref{eq:chemical-potential-standard}) for each of the three species and noting that the contributions of the momenta cancel. As discussed below, various alchemical protocols exist to evaluate the ratios of partition functions in Eq.~(\ref{eq:DG0-binding-constant-def}), providing a connection between the theory and observed binding affinities.
